---
title: "writing_functions"
author: "Fang Liu"
date: "11/10/2021"
output: html_document
---

Load required packages. 
```{r, message = FALSE}
library(tidyverse)
library(rvest)

set.seed(1)
```

### My first function!
```{r}
x_vec = rnorm(25, mean = 5, sd = 3)

(x_vec - mean(x_vec)) / sd(x_vec)
```

When I want to do this multiple times, I can use a function. 
```{r}
z_scores = function(x) {
  z = (x - mean(x)) / sd(x)
  z
}

z_scores(x_vec)
```

Test the function:
```{r, eval=FALSE}
z_scores(3)
z_scores("hello")
z_scores(iris)
z_scores(sample(c(TRUE, FALSE), 25, replace = TRUE))
```

We want to "fail noisily and as soon as possible".... Thus, we can add some checks on the argument values using conditional statements
```{r}
z_scores = function(x) {
  
  if (!is.numeric(x)){
    stop("Argument x should be a numeric")
  } else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  
  z = (x - mean(x)) / sd(x)
  z
}

z_scores(x_vec)
```


### Multiple OUTPUTS 

What if we want to return the mean and standard deviation?
Option 1: store each of the variables in a named list and return that list
```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)){
    stop("Argument x should be a numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  list(mean = mean_x, 
       sd = sd_x)
}

mean_and_sd(x_vec)
```

Option 2: store values in a data frame (easier to use other tools :) 
```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)){
    stop("Argument x should be a numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
}

mean_and_sd(x_vec)
```

### Multiple INPUTS 

Example: take a sample size along with a true mean and sd, simulates data from a normal distribution and return the estimated mean & sd
```{r}
sim_data = tibble(
  x = rnorm(30, mean = 2, sd = 3)
)

sim_data %>% 
  summarize(
    mu_hat = mean(x),
    sigma_hat = sd(x)
  )
```

But... what if I want to change the sample size and parameters (i.e., the arguments)
```{r}
sim_mean_sd = function(n, mu = 2, sigma = 3){
  
  sim_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma),
  )
  
  sim_data %>% 
    summarize(
      mu_hat = mean(x),
      sigma_hat = sd(x)
    )
}

sim_mean_sd(10)
sim_mean_sd(1000)

#as sample sample increases, the mean and sd gets closer to the "true" value
```

Two type of argument matching: 
1) positional matching: sim_mean_sd(30, 5, 1)
2) named matching: sim_mean_sd(sd = 1, n = 30, mu = 5) 
*Named arguments can be supplied in any order!

### Revisiting some past examples  
Write a function to scrape review information for any URL to an Amazon review page
```{r}
read_page_reviews <- function(url) {
  
  html = read_html(url)
  
  review_titles = 
    html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()
  
  review_text = 
    html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim()
  
  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
}
```

Next, use this function to read in reviews from a few pages and combine the results 
```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

vec_urls = str_c(url_base, 1:5)

dynamite_reviews = bind_rows(
  read_page_reviews(vec_urls[1]),
  read_page_reviews(vec_urls[2]),
  read_page_reviews(vec_urls[3]),
  read_page_reviews(vec_urls[4]),
  read_page_reviews(vec_urls[5])
)

dynamite_reviews
```

### Functions as arguments  
Ability to pass **functions** as arguments into functions?  

Example: function that takes a vector and function as input and returns the results of applying that function to the vector input
```{r}
x_vec = rnorm(25, 0, 1)

my_summary = function(x, summ_func) {
  summ_func(x)
}

#test the function
my_summary(x_vec, sd)
my_summary(x_vec, IQR)
my_summary(x_vec, var)
```

### Scoping and names  
```{r}
f = function(x){
  z = x + y
  z
}

x = 1
y = 2

f(x = y)

#f(x= 2) --> function(2); return z = 2 + 2 = 4??
```

In this example, we define a variable in global environment and use it in your function... but it isn't passed as a argument... 




